### 2019-05-05 Sections/intro_to_QIT.tex
intro to qit
QIT + 1 added bib

\section{Introduction to quantum information theory}\index{Quantum information theory}

@@

``Information theory begins with the observation that there is a fundamental link between probabilities and information."

With a given event (whose value is a random variable $X$), suppose that it has a set of outcomes $\{x\}$, each occuring with probability 
$\{p_x \}$. Then the \textit{Shannon entropy} associated with the random variable is defined as

\begin{align}\index{Shannon entropy}
H(X) = -\sum_x p_x\log_2(p_x).
\end{align}

@@

\begin{figure}[!hbtp]
%\includegraphics[clip=true, width=0.4\textwidth]{classical_mutual_info.pdf}
\captionspacefig \caption{\label{fig:mutual_info}}	
\end{figure}

>>>>

\section{Brief introduction to quantum information theory}\index{Quantum information theory}

@@

``Information theory begins with the observation that there is a fundamental link between probabilities and information"\cite{barnett2009quantum}.

Suppose that there are two parties trying to communicate, conventionally named Alice and Bob. Alice 
sends information using an alphabet $\{x_j \}$, and each letter occurs with probability $p_j$. If
some letter occur less likely than others, then Bob will be more surprised receiving those, and one
might naturally expect that the information content of those events are higher.

This suggests a way to measure the \textit{information content} of an outcome, or how surprised Bob is:

\begin{align}
i(x_j) \equiv \log\left(\frac{1}{p(x_j)}  \right) =  -\log\left(p(x_j)  \right)
\end{align}

We can model Alice's source as a random variable $X$, whose outcomes
are $\{ x_j\}$ each occuring with probability $p_j$.
Then the expected information content of the source, or \textit{Shannon entropy} 
associated with the $X$ is defined as

\begin{align}\index{Shannon entropy}
H(X) = -\sum_i p_i\log_2(p_i).
\end{align}

@@

\begin{figure}[hbt]
\includegraphics[clip=true, width=0.4\textwidth]{classical_mutual_info.pdf}
\captionspacefig \caption{\label{fig:mutual_info}}	
\end{figure}
